SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on Disks

### 2015-04-30 papers/B1555_EdgeOn/B1555_letter.tex
update expdisk model
update changes from John except Data part

\title[Beware the Effect of Edge-on Disks]{
%Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375
SHARP II: Dark Matter Substructure, Gravitational Lens Flux Ratio
Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
Disks
}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
jwhsueh@ucdavis.edu (JWH); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\\
$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
Davis, CA 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

Gravitational lens flux-ratio anomalies provide a powerful technique
for detecting the presence of dark matter substructure in distant
galaxies.  However, before using the statistics of systems with these
anomalies, it is imperative to ascertain that a given system does not
have properties that could plausibly cause the observed anomaly
without the need for substructure.  In this letter, we present the
case of the B1555+375 lens system, which has a strong radio-wavelength
flux-ratio anomaly but where the lensing galaxy is also revealed in
high-resolution infrared imaging to have a clear edge-on disk component.  The
disk crosses directly over the pair of images that exhibit the
anomaly, and we show that simple models that include the disk can
reproduce the anomaly without requiring substructure.  
Other lens systems that we have observed with adaptive optics imaging
as part of the Strong lensing at High Angular Resolution Programme (SHARP)
show a similar behaviour and will be the subject of a future paper.  
These results suggest that the assumption that
all flux-ratio anomalies are due to substructure will likely overestimate
the substructure fraction in massive galaxies.

@@

A common feature of simulations of structure formation is the presence
of thousands of subhalos that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane and the latest discovery of new dwarf galaxies \citep{DES15,Kop15}.  
This is the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
understand this discrepancy, it is imperative to build up a large
sample of satellites/subhalos in galaxies outside the Local Group.
 However, this process is challenging due to the faintness of the satellite
galaxies.  Furthermore, lower-mass satellites may not be able to
retain the gas needed for ongoing star formation \citep[e.g.,][]{P11},
rendering them effectively dark.  These factors make gravitational
lensing a powerful and promising tool for the detection of
substructure.

It was first suggested by \citet{Mao1998} that flux ratio anomalies
observed in radio loud multiple images of lensed quasars could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are not sensitive to microlensing from
stars nor dust extinction. This makes flux ratio anomalies a promising
tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002, N13}.  At
present, the amount of substructure derived from flux ratio anomalies
is in disagreement with predictions from numerical simulations, with
the former requiring a larger fraction of mass in substructure than
expected \citep{Xu14}. While this could be the result of small sample
statistics, it could also be an indication that flux ratio anomalies
have a different origin than substructure.
%
An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

While future large-scale surveys, such as the LSST, are expected to
deliver new large samples of gravitationally lensed quasars, in the
near future the discovery of new systems using narrow-line quasar
emission \citep{N14} will provide new invaluable statistical
perspective on current constraints based on flux ratio anomalies.  In
this letter, we explore the idea that not all flux ratio anomalies are
related to the presence of substructure, but that some originate in a
more complex lens galaxy mass distribution than initially
considered. To this end we use new infra-red data from the Strong
lensing at High Angular Resolution Program 
\citep[SHARP;][Fassnacht et al., in prep]{SHARP12}.
The main goal of the SHARP project is to re-observe known
quadruple and Einstein ring lens systems at high angular
resolution by making use of observations with (1) adaptive optics (AO)
on the Keck telescopes, (2) the Hubble Space Telescope, and (3) large
interferometric arrays \citep{SHARP12,V12}. In particular, to better
understand the causes of flux ratio anomalies in gravitational lenses
we focus on the B1555+375 lens system\citep{Marlow99}.  This system was
discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
has a pair of merging images that show a strong flux ratio anomaly at
radio wavelengths.  Follow-up observations ruled out radio propagation
effects as the cause of the anomaly \citep{K03,KD04}.  The B1555+375
system was included in both the observational and theoretical analysis
of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
mass distribution is of key importance.  Our analysis makes use of
the new information obtained from the latest SHARP infrared imaging.
The paper is organized as follows: the  SHARP data are
introduced in section 2; in section 3 we present the lens model while
the results of this analysis and their implications are discussed in
section 4.

@@

\begin{figure*}
%\begin{minipage}{140mm}
%\includegraphics[width=140mm]{B1555_gallery.eps}
\includegraphics[width=0.95\textwidth]{B1555_gallery.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the figures show data from
HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.
\label{fig:multiband}}
%
%\end{minipage}

@@

The B1555+375 system was observed using the NIRC2 camera on the Keck 2
Telescope on the night of 2012 May 16 UT.  The adaptive optics system
was used, with the corrections derived from the laser guide star and a
$R$=14.4 tip-tilt \textbf{star} that was located 45$^{\prime\prime}$ from the lens
system.  The ``narrow camera'' mode was used, giving a field of view
of roughly 10$^{\prime\prime}$\ on a side and a pixel scale of 10~mas.
Six dithered 300~s exposures were obtained in $K^{\prime}$ band.  The
data were reduced with the standard SHARP pipeline, which is a
python-based package that is a refinement of the process described in
\citet{Auger_EELS1}.  A cutout of the final reduced image is shown in
Fig.~\ref{fig:multiband} and again in Fig.~\ref{fig:merlin} with
contours from the MERLIN radio observations of \citet{Marlow99}
overlaid.  There are several notable features in the Keck AO data.
These include the nearly complete lack of emission associated with the
B and D lensed images, as can be seen by comparing the radio contours
to the $K^\prime$-band emission, and faint but clearly visible
emission from what appears to be an edge-on lensing galaxy.

@@

The B1555+375 system was also observed by the Hubble Space Telescope
(HST) in three broad bands.  The optical data were obtained with the
Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands
(GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object
Spectrograph (NICMOS) was used to observe the system in the $F160W$
band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
obtained with the NIC2 camera.  We reduced all of the archival HST
data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
  MATT], producing final drizzled images with pixel scales of 50~mas.
The reduced images are shown in Figure~\ref{fig:multiband}.  The lens
system is not detected at high significance in the optical bands, but
is clearly seen in the NICMOS $F160W$ image.  The edge-on lensing
galaxy stands out in the NICMOS image.

The observation details of Keck AO and HST imaging are shown in Table 1.

@@

 \hline
   HST				&		WFPC2    &  F555W		&	2000/10/09 	&	5200\\
   HST				&		WFPC2    &  F814W		&	2000/10/09 &	5200\\
   HST				&		NICMOS/NIC2	&	F160W	&	2003/11/02 & 5376\\
   Keck2			&		NIRC2 AO	&   $K^\prime$	& 2012/05/16	&  1800\\
   \hline
\end{tabular}
%\end{minipage}
\end{table}

@@

\section{Lens Modeling}

To model B1555+375, we use the lens modeling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image
positions and flux densities measured by the radio observations of
\citet{Marlow99}.  These authors present a singular isothermal ellipsoid
(SIE) model that provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A
and B.  \citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  Although
the flux ratio anomaly that is observed in the radio data may be
caused by substructure in the lensing galaxy, our high-resolution near
infrared imaging suggests another explanation.  In both the $K^\prime$
band adaptive optics data and the HST infrared imaging (two rightmost panels in
Fig. 1), the lensing galaxy has a clear edge-on disk component with a
position angle of $\approx 10$ degree.  We therefore model the system
with a disk component in order to see if such a model can explain the
flux ratio anomaly without the need for substructure.  The edge-on
disk may also explain the system morphology that is observed in the
near infrared imaging.  In particular, neither image B nor image D is
detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
these lensed images lie on or close to the edge-on disk.  Thus, strong
extinction in the disk could cause the lack of detection of these
images.

As a first trial of modeling, we create a single SIE model to check
the performance of a simple lensing potential. Consistent with
previous studies \citep{Marlow99, Xu14}, our single elliptical
potential model cannot predict the flux anomaly in B1555+375.  We then
create two separate models of the lensing potential that both
incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
and an exponential edge-on disk (SIE+expdisk).  In the second model
the disk is represented as a very elongated SIE component (2-SIE).
The lens system is red, with a strong jump in flux between the F814W
(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so
we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
$z_s =1.5$. \textbf{This assumption on redshifts is due to that some lens model parameters contain distance information. Our choice of redshifts does not affects the predicted magnifications nor flux ratios.} Our steps to explore the parameter space are: (1) Apply
strong priors from the SHARP AO image to the edge-on disk position angle
and ellipticity, and use the best-fit model of \citet{Marlow99} as the
starting point for the bulge\textbf{/halo} component and the source position. (2)
Let all parameters without priors vary to reach a temporary best
fit. (3) Start with the best fit in step 2 and let all parameters with
priors vary to reach another best fit (also ensure this best fit is
not far from the priors). (4) Let all parameters vary to reach the
final optimal model.  The full best-fit parameters are shown in Table
2. Both of these models produce lensed images with positions and
fluxes that are good matches to the radio observations.  While both of
the two component models produce significantly improved matches to the
fluxes than the single SIE model, the 2-SIE version has a somewhat
better performance than the SIE+expdisk model in reproducing flux
ratios. The comparison of the observations and our lens modeling is
given in Figure 3 and Tables 3 \& 4.  We have not included an external
shear component into our model because the constraints provided by the
image positions and fluxes would not be sufficient to constrain such a
model. However, we note that the image not affected by dust (image C)
in the Keck AO data is consistent with negligible shear (i.e. shear
strength $\Gamma_s=0.002$), when modeled with the pixelized technique
of \citet{V09}.

@@

\begin{figure}
%\plotone{point_source.eps}
\includegraphics[width=84mm]{point_source.eps}
\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle. \label{fig2}}
\end{figure}

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens models.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	  & $-0.1833$	& $-0.1884$  \\
$y_1$	  &$-0.1945$	&$-0.1607$  \\

$\sigma_1$ &$140.3$     & $145.3$ \\
$e_1$	  & $0.27$	& $0.24$ \\
$\theta_1$ &$105.5 \degr$ & $99.5 \degr$ \\
\hline
$x_2$	  &$-0.1615$ 	&$-0.1594$  \\
$y_2$	  &$-0.2402$	& $-0.2225$  \\
$M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
$\sigma_2$ & ...        &$122.7$ \\  
$e_2$	  &$0.84$	&$0.82$  \\
$\theta_2$ &$7.7\degr$ &$6.5\degr$  \\
$r_e$	  & $0.19 ''$ &  ... \\
\hline
%$\chi ^2$ & $1.05$ & $0.04$ \\
%\hline
\end{tabular}

%\end{minipage}
\medskip
Subscripts 1 and 2 represent bulge\textbf{/halo} and disk components in each model respectively. Positions are offsets from radio image component A measured in units of arcsec. The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$. $e$ is ellipticity and $\theta$ is the position angle measured east of north.

@@

\begin{table*}
%\centering
 \begin{minipage}{140mm}
  \caption{Radio observation and model-predicted lensed image positions.}
  \begin{tabular}{@{}ccccccc}

@@

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
					 &East &North &East 		&North &East 		&North\\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0480$ & $-0.0726 $  &  $+0.0480$  \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$  & $-0.4117 $  &   $+0.0280$ \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1620$ &$-0.3680$  & $-0.1619$    &  $+0.3680$ \\  
\hline
\end{tabular}

@@

Comparison between radio and model-predicted lensed image positions. Observation data quoted from Table 2 in \citet{Marlow99}. Position offsets are in unit of arcsec. Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.

@@

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Flux ratios of B1555+375 components.}
  \begin{tabular}{@{}ccccccc}

\hline
	& MERLIN  & \multicolumn{3}{c}{Model}\\
		&5 GHz   & 1-SIE & SIE+expdisk & 2-SIE\\
\hline
$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.70$ & $1.61$ \\ 
$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $1.42$ & $1.97$\\
$f_A/f_D$		&$11.62 (3.24)$  &$9.82$& $5.84$ & $11.63$\\

@@

%\end{minipage}
\medskip
Comparison between radio data and model-predicted flux ratios. The radio flux ratios and errors are from Table 1  in \citet{K03}.

@@

Gravitational lensing is, at present, the most powerful tool for
studying substructure in galaxies outside of the Local Universe, and
the flux ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes, such as
propagation effects and assumptions about the mass distribution of the
lens galaxy.  It is for this reason that much of the effort in the
flux-ratio technique has been focused on radio-loud lens systems.  At
these wavelengths, dust extinction and microlensing effects should be
minimal \citep[although see][for a rare example of radio
  microlensing]{K2000}.  Radio propagation effects can affect radio
fluxes, as is clearly shown in the B0128+437 system \citep{B04}.
However, these propagation effects can be disentangled from
substructure lensing because they have well known dependencies on
wavelength. \citet{KD04} examine all eight radio loud flux anomalous
lenses besides B0128+437, namely: MG 0414+0534, B0712+472, B1359+154,
B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265.  They found
no strong wavelength dependence in the flux ratios of all these
systems and therefore rule out radio propagation effects as
significant contributors to the observed anomalies.

>>>>

\title[Beware the Effect of Edge-on Disks]{
%Gravitational Lens Modelling of flux-ratio Anomalous System B1555+375
SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio
Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
Disks
}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
jwhsueh@ucdavis.edu (JWH); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\\
$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
Davis, CA 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

Gravitational lens flux-ratio anomalies provide a powerful technique
for detecting the presence of dark matter substructure in distant
galaxies.  However, before using the statistics of systems with these
anomalies, it is imperative to ascertain that a given system does not
have properties that could plausibly cause the observed anomaly
without the need for substructure.  In this letter, we present the
case of the B1555+375 lens system, which has a strong radio-wavelength
flux-ratio anomaly but where the lensing galaxy is also revealed in
high-resolution infrared imaging to have a clear edge-on disk component.  The
disk crosses directly over the pair of images that exhibit the
anomaly, and we show that simple models that include the disk can
reproduce the anomaly without requiring substructure.  
%Other lens systems that we have observed with adaptive optics imaging
%as part of the Strong lensing at High Angular Resolution Programme (SHARP)
%show a similar behaviour and will be the subject of a future paper.  
These results suggest that the assumption that
all flux-ratio anomalies are due to substructure will likely overestimate
the substructure fraction in massive galaxies.

@@

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane and the latest discovery of new dwarf galaxies \citep{DES15,Kop15}.  
This is the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
understand this discrepancy, it is imperative to build up a large
sample of satellites/subhaloes in galaxies outside the Local Group.
 However, this process is challenging due to the faintness of the satellite
galaxies.  Furthermore, lower-mass satellites may not be able to
retain the gas needed for ongoing star formation \citep[e.g.,][]{P11},
rendering them effectively dark.  These factors make gravitational
lensing a powerful and promising tool for the detection of
substructure.

It was first suggested by \citet{Mao1998} that flux-ratio anomalies
observed in radio-loud multiple images of lensed quasars could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux-ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are not sensitive to microlensing from
stars nor dust extinction. This makes flux-ratio anomalies a promising
tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002}.  At
present, the amount of substructure derived from flux-ratio anomalies
is in disagreement with predictions from numerical simulations, with
the former requiring a larger fraction of mass in substructure than
expected \citep{Xu14}. While this could be the result of small sample
statistics, it could also be an indication that flux-ratio anomalies
have a different origin than substructure.
%
An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a,V12}.

%While future large-scale surveys, such as the LSST, are expected to
%deliver new large samples of gravitationally lensed quasars, in the
%near future the discovery of new systems using narrow-line quasar
%emission \citep{N14} will provide new invaluable statistical
%perspective on current constraints based on flux-ratio anomalies.  
In this letter, we explore the idea that not all flux-ratio anomalies are
related to the presence of substructure, but that some originate in a
more complex lens galaxy mass distribution than initially
considered. To this end we use new infra-red data from the Strong
lensing at High Angular Resolution Program 
\citep[SHARP;][Fassnacht et al., in prep]{SHARP12}.
The main goal of the SHARP project is to re-observe known
quadruple and Einstein ring lens systems at high angular
resolution by making use of observations with (1) adaptive optics (AO)
on the Keck telescopes, (2) the Hubble Space Telescope, and (3) large
interferometric arrays \citep{SHARP12,V12}. In particular, to better
understand the causes of flux-ratio anomalies in gravitational lenses
we focus on the B1555+375 lens system\citep{Marlow99}.  This system was
discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
has a pair of merging images that show a strong flux-ratio anomaly at
radio wavelengths.  Follow-up observations ruled out radio propagation
effects as the cause of the anomaly \citep{K03,KD04}.  The B1555+375
system was included in both the observational and theoretical analysis
of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
mass distribution is of key importance.  Our analysis makes use of
the new information obtained from the latest SHARP infrared imaging.
The paper is organized as follows: the  SHARP data are
introduced in section 2; in section 3 we present the lens model while
the results of this analysis and their implications are discussed in
section 4.

@@

\begin{figure*}
%\begin{minipage}{140mm}
%\includegraphics[width=140mm]{B1555_gallery.eps}
\includegraphics[width=0.95\textwidth]{B1555_gallery.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3.7 arcsec on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the panels show data from
\textit{HST}/WFPC2 in the F555W band, \textit{HST}/WFPC2 in the F814W band, \textit{HST}/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.
\label{fig:multiband}}
%
%\end{minipage}

@@

The B1555+375 system was observed using the NIRC2 camera on the Keck 2
Telescope on the night of 2012 May 16 UT.  The adaptive optics system
was used, with the corrections derived from the laser guide star and a
$R$=14.4 tip-tilt \textbf{star} that was located 45 arcsec from the lens
system.  The narrow camera mode was used, giving a field of view
of roughly 10 arcsec on a side and a pixel scale of 10~mas.
Six dithered 300~s exposures were obtained in the $K^{\prime}$ band filter.  The
data were reduced with the standard SHARP pipeline, which is a
python-based package that is a refinement of the process described in
\citet{Auger_EELS1}.  A cutout of the final reduced image is shown in
Fig.~\ref{fig:multiband} and again in Fig.~\ref{fig:merlin} with
contours from the MERLIN radio observations of \citet{Marlow99}
overlaid.

There are several notable features in the Keck AO data.
These include the nearly complete lack of emission associated with the
B and D lensed images, as can be seen by comparing the radio contours
to the $K^\prime$-band emission, and faint but clearly visible
emission from what appears to be an edge-on lensing galaxy.

@@

The B1555+375 system was also observed with the \textit{Hubble Space Telescope
(\textit{HST})} in three broad bands.  The optical data were obtained with the
Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands
(GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object
Spectrograph (NICMOS) was used to observe the system in the $F160W$
band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
obtained with the NIC2 camera.  We reduced all of the archival \textit{HST}
data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
  MATT], producing final drizzled images with pixel scales of 50~mas.
The reduced images are shown in Figure~\ref{fig:multiband}.  The lens
system is not detected at high significance in the optical bands, but
is clearly seen in the NICMOS $F160W$ image \textbf{where the edge-on lensing
galaxy clearly stands out.}

The observation details of Keck AO and \textit{HST} imaging are shown in Table 1.

@@

 \hline
   \textit{HST}				&		WFPC2    &  F555W		&	2000/10/09 	&	5200\\
   \textit{HST}				&		WFPC2    &  F814W		&	2000/10/09 &	5200\\
   \textit{HST}				&		NICMOS/NIC2	&	F160W	&	2003/11/02 & 5376\\
   Keck2			&		NIRC2 AO	&   $K^\prime$	& 2012/05/16	&  1800\\
   \hline
\end{tabular}
%\end{minipage}
\end{table}

@@

\section{Lens modelling}

To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image
positions and flux densities measured by the radio observations of
\citet{Marlow99}, \textbf{who also} presented a singular isothermal ellipsoid
(SIE) model that provided the first fit[a good fit--John/ but It's not good compare to our model--JW] to the image positions but
does not reproduce the strong flux-ratio anomaly between components A
and B.  %\citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  
Although the flux-ratio anomaly that is observed in the radio data \textbf{implies there must be some perturbation to the mass model, which} may be
caused by substructure in the lensing galaxy, our high-resolution near
infrared imaging suggests another explanation.  In both the $K^\prime$
band adaptive optics data and the \textit{HST} infrared imaging (\textbf{see} in
Fig. 1), the lensing galaxy has a clear edge-on disk component with a
position angle of $\approx 10$ degree.  We therefore model the system
with a disk component in order to see if such a model can explain the
flux-ratio anomaly without the need for substructure.  The edge-on
disk may also explain the system morphology that is observed in the
near infrared imaging.  In particular, neither image B nor image D is
detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
these lensed images lie on or close to the edge-on disk.  Thus, strong
extinction in the disk could cause the \textbf{non-}detection of these
images.

As a first trial of modelling, we create a single SIE model to check
the performance of a simple lensing potential. Consistent with
previous studies \citep{Marlow99, Xu14}, our single elliptical
potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.  We then
create two separate models of the lensing potential that both
incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
and an exponential edge-on disk (SIE+expdisk).  In the second model
the disk is represented as a very elongated SIE component (2-SIE).
The lens system is red, with a strong jump in flux between the F814W
(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so
we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
$z_s =1.5$. \textbf{This assumption on redshifts is due to that some lens model parameters contain distance information. Our choice of redshifts does not affects the predicted magnifications nor flux-ratios.}

Our steps to explore the parameter space are: (1) Apply
strong priors from the SHARP AO image to the edge-on disk position angle
and ellipticity, and use the best-fit model of \citet{Marlow99} as the
starting point for the bulge\textbf{/halo} component and the source position. (2)
Let all parameters without priors vary to reach a temporary best
fit. (3) Start with the best fit in step 2 and let all parameters with
priors vary to reach another best fit (also ensure this best fit is
not far from the priors). (4) Let all parameters vary to reach the
final optimal model.  The full best-fit parameters are shown in Table
2. Both of these models produce lensed images with positions and
fluxes that are good matches to the radio observations.  While both of
the two component models produce significantly improved matches to the
fluxes than the single SIE model, the 2-SIE version has a somewhat
better performance than the SIE+expdisk model in reproducing flux
ratios. The comparison of the observations and our lens modelling is
given in Figure 3 and Tables 3 \& 4.  We have not included an external
shear component into our model because the constraints provided by the
image positions and fluxes would not be sufficient to constrain such a
model. However, we note that the image not affected by dust (image C)
in the Keck AO data is consistent with negligible shear (i.e. shear
strength $\Gamma_s=0.002$), when modeled with the pixelized technique
of \citet{V09}.

@@

\begin{figure}
%\plotone{point_source.eps}
\includegraphics[width=84mm]{point_source.eps}
\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model [NOT UPDETED YET], marked by a black filled circle. \label{fig2}}
\end{figure}

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens models. Subscripts 1 and 2 represent bulge\textbf{/halo} and disk components in each model respectively. Positions are offsets from radio image component A measured in units of arcsec. The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	  & $-0.1794$	& $-0.1884$  \\
$y_1$	  &$-0.1881$	&$-0.1607$  \\

$\sigma_1$ &$140.3$     & $145.3$ \\
$e_1$	  & $0.21$	& $0.24$ \\
$\theta_1$ &$73.6 \degr$ & $99.5 \degr$ \\
\hline
$x_2$	  &$-0.1639$ 	&$-0.1594$  \\
$y_2$	  &$-0.2542$	& $-0.2225$  \\
$M_{tot,2}$  & $3.58\times 10^{10} $  & ...	 \\  
$\sigma_2$ & ...        &$122.7$ \\  
$e_2$	  &$0.84$	&$0.82$  \\
$\theta_2$ &$4.0\degr$ &$6.5\degr$  \\
$r_e$	  & $0.21 ''$ &  ... \\
\hline
%$\chi ^2$ & $1.05$ & $0.04$ \\
%\hline
\end{tabular}

%\end{minipage}

@@

\begin{table*}
%\centering
 \begin{minipage}{140mm}
  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec). Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.}
  \begin{tabular}{@{}ccccccc}

@@

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
					 &East &North &East 		&North &East 		&North\\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0723$ &$+0.0480$ & $-0.0726 $  &  $+0.0480$  \\  
C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4114$ &$-0.0282$  & $-0.4117 $  &   $+0.0280$ \\  
D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1631$ &$-0.3628$  & $-0.1619$    &  $+0.3680$ \\  
\hline
\end{tabular}

@@

@@

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios.}
  \begin{tabular}{@{}ccccccc}

\hline
	& MERLIN  & \multicolumn{3}{c}{Model}\\
		&5 GHz   & 1-SIE & SIE+expdisk & 2-SIE\\
\hline
$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.62$ & $1.61$ \\ 
$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $2.89$ & $1.97$\\
$f_A/f_D$		&$11.62 (3.24)$  &$9.67$& $9.30$ & $11.63$\\

@@

%\end{minipage}
\medskip

@@

Gravitational lensing is, at present, the most powerful tool for
studying substructure in galaxies outside of the Local Universe, and
the flux-ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux-ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes, such as
propagation effects and assumptions about the mass distribution of the
lens galaxy.  It is for this reason that much of the effort in the
flux-ratio technique has been focused on radio-loud lens systems.  At
these wavelengths, dust extinction and microlensing effects should be
minimal \citep[although see][for a rare example of radio
  microlensing]{K2000}.  \textbf{Also,  scatter broadening} can affect radio
fluxes, as is clearly shown in the B0128+437 system \citep{B04}, and free-free absorption can change the flux-ratios as a function of frequency,
for example, B0218+357 \citep{M07}.
However, these propagation effects can be disentangled from
substructure lensing because they have well known dependencies on
wavelength. \citet{KD04} examine all eight radio-loud flux anomalous
lenses besides B0128+437, namely: MG 0414+0534, B0712+472, B1359+154,
B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265.  They found
no strong wavelength dependence in the flux-ratios of all these
systems and therefore rule out radio propagation effects as
significant contributors to the observed anomalies.

In this letter, we focus on the effect of more complicated mass
distributions for the lens galaxy on flux-ratio anomalies.
Traditionally, flux anomalous lensed quasars are radio-loud systems
that are firstly discovered in radio observations. While radio data
provide reliable information on the positions and the fluxes of the
lensed images, they are often unable to detect the lens
galaxies. Moreover, lens modelling based only on the positions of the
four images can be highly degenerate and prior assumptions play a key
role in the interpretation of the observed flux-ratio anomaly.  Since
lens galaxies are typically at redshifts of $z \leq 1$, optical and
near-infrared observations are ideal for measuring the light distribution
of lens galaxies and obtaining useful prior information on the underlying
mass distributions. Indeed \citet{SHARP12} showed that high
resolution IR imaging can help to significantly improve the precision
of the lens modelling. This improvement is even more dramatic in the
case of B1555+375, where \textit{HST} and SHARP AO high resolution imaging has
allowed us to detect, for the fist time, the presence of an edge-on
disk. This newly discovered edge-on disk provides a strong prior for our
lens modelling.  With \textbf{an additional disk component}, our models produce
matches to both the radio image positions and their flux-ratio, while
models with only one SIE component \citep{Marlow99,Xu14} fail to
reproduce the fluxes correctly. Our successful modelling indicates
that the kiloparsec-scale structure of the lens galaxy itself is
sufficient to explain the flux-ratio anomalies in B1555+375, without
any need to invoke the presence of substructure.
